\documentclass[a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[english]{babel}
\usepackage{ClearSans}

\pagestyle{empty}

\renewcommand{\familydefault}{\sfdefault}

\newcommand{\cvauthorvar}{}

\newcommand{\cvtitlelocationvar}{}

\newcommand{\cvlinkedinvar}{}

\newcommand{\cvemailvar}{}

\newcommand{\cvphonevar}{}

\newcommand{\cvauthor}[1]{\renewcommand{\cvauthorvar}{#1}}

\newcommand{\cvtitlelocation}[1]{\renewcommand{\cvtitlelocationvar}{#1}}

\newcommand{\cvlinkedin}[1]{\renewcommand{\cvlinkedinvar}{https://linkedin.com/in/#1}}

\newcommand{\cvemail}[1]{\renewcommand{\cvemailvar}{#1}}

\newcommand{\cvphone}[1]{\renewcommand{\cvphonevar}{#1}}


\newcommand{\cvtitle}{
  \begin{center}
    {\Large\textbf{\cvauthorvar}}
    \vspace{8pt}
    
    \begin{tabular}{ll}
      \cvemailvar & \cvphonevar \\
      \cvlinkedinvar & \cvtitlelocationvar
    \end{tabular}
  \end{center}
}

\newcommand{\invalidmonth}{\emph{\textbf{invalid-month}}}

\newcommand{\cvmonth}[1]{
  \ifcase#1 \invalidmonth
    \or Jan
    \or Feb
    \or Mar
    \or Apr
    \or May
    \or Jun
    \or Jul
    \or Aug
    \or Sep
    \or Oct
    \or Nov
    \or Dec
  \else
    \invalidmonth
  \fi
}

\newcommand{\cvdate}[2]{
  \emph{\cvmonth{#1}} {#2}
}

\newcommand{\cvposition}[2]{
  \noindent\textbf{#1 at #2}\par
}

\newcommand{\present}{
  \emph{Present}
}

\newcommand{\cvlocation}[3]{
  \noindent #1, #2 -- #3\par
}

\newenvironment{cveducation}{
  \noindent{\large\textbf{Education:}}
  \begin{itemize}
}{
  \end{itemize}
  \bigskip
}

\newcommand{\cveducationitem}[4]{
  \item \textbf{#1}, #2, #3 \\#4
}

\newenvironment{cvexperience}{
  \noindent{\large\textbf{Work Experience:}}
  \medskip
}{
  \bigskip
}

\newenvironment{cvjob}{
  \begin{sloppypar}
}{
  \end{sloppypar}
  \bigskip
}

\newenvironment{cvlang}{
  \noindent{\large\textbf{Languages:}}
  \begin{itemize}
}{
  \end{itemize}
  \bigskip
}

\newcommand{\cvlangitem}[2]{
  \item \textbf{#1} -- \emph{#2}
}

\newcommand{\cvskills}[1]{\texttt{(#1)}}

\begin{document}

\cvauthor{Walber Zaldivar Herrera}
\cvtitlelocation{Neptunia, Canelones, Uruguay}
\cvlinkedin{walber-zaldivar-herrera}
\cvphone{+598~9505~9121}
\cvemail{walber.zaldivar@gmail.com}

\cvtitle

\begin{cveducation}
  \cveducationitem{Higher Institute of Technologies and Applied Sciences}
  {Havana, Cuba}{\cvdate{7}{2004}}
  {BEng. in Nuclear and Energy Technologies \emph{(Cum Laude)}}

  \cveducationitem{Vocational Pre-University Institute of Exact Sciences V. I. Lenin}
  {Havana, Cuba}{\cvdate{7}{1998}}
  {High School}
\end{cveducation}

\begin{cvexperience}

  \begin{cvjob}
    \cvposition{Software Developer Engineer}{Dualboot Partners}
    \cvlocation{Remote}{\cvdate{4}{2023}}{\cvdate{2}{2024}}
    \begin{itemize}
      \item Staff augmentation, Delivery Services Provider -- \emph{Marketplace Integration Team}, \emph{US Client}
      \begin{itemize}
        \item Participated in the definition and development of integrations with external vendors, customization, 
        feature implementation, and bug-fixing. \cvskills{Scala, Kotlin, Micronaut, MySQL, PostgreSQL, Docker, Git, JavaScript}
        \item Deployed to production and lower environments, monitor correct behavior. 
        \cvskills{Jenkins, Docker, GitHub Actions, Grafana}
        \item Offered support to the \emph{Market Operations Team}.
        \item Prepared base \emph{mountebank} configuration for usage as part of automated tests. \cvskills{Mountebank, Docker, GitHub Actions}
      \end{itemize}
    \end{itemize}
  \end{cvjob}
  
  \begin{cvjob}
    \cvposition{Senior Software Developer Engineer}{SensorData}
    \cvlocation{Remote (part-time)}{\cvdate{10}{2022}}{\cvdate{9}{2023}}
    \begin{itemize}
      \item Led the migration of React Native Android applications to Kotlin for custom Android devices, improving 
      performance and adhering to best practices. \cvskills{Kotlin, Hilt, Room, MQTT, Retrofit, OkHttp, Moshi, Git}
    \end{itemize}
  \end{cvjob}

  \begin{cvjob}
    \cvposition{Senior Software Developer Engineer}{BairesDev}
    \cvlocation{Remote}{\cvdate{11}{2021}}{\cvdate{3}{2023}}

    \begin{itemize}
      \item Staff augmentation, Background Screening Services Provider, \emph{US Client}\\\cvdate{11}{2021}--\cvdate{2}{2023}
      \begin{itemize}
        \item Contributed to the migration of a desktop solution to the web. \cvskills{Kotlin, Spring Boot, JUnit5, 
        Mockito, Docker, GraphQL, PostgreSQL, TypeScript, React, Git}
      \end{itemize}
      \item Bench, \cvdate{3}{2023}
      \begin{itemize}
        \item Self-training on Git, Java, Angular, SQL, and AWS during the bench period. \cvskills{Git, Java, Angular, SQL, AWS}
      \end{itemize}
    \end{itemize}
  \end{cvjob}

\begin{cvjob}
\cvposition{Senior Software Developer Engineer}{Endava}
\cvlocation{Remote}{\cvdate{1}{2021}}{\cvdate{10}{2021}}

\begin{itemize}
  \item Bench, \cvdate{1}{2021}--\cvdate{2}{2021}
  \begin{itemize}
    \item Led a small team in developing a toy calendar project to enhance skills during the bench period. 
    \cvskills{Java, Spring Boot, Jacoco, SonarQube}
  \end{itemize}
  \newpage
  \item Staff augmentation, Global Provider of Electronic Payments Solutions, \cvdate{3}{2021}--\cvdate{6}{2021}
  \begin{itemize}
    \item Contributed to the customization, features implementation, and bug-fixing of payment devices software. 
    \cvskills{C/C++, Python, Git}
    \item Implemented an \emph{ISO8583} messages parser to enhance QA productivity for the Endava QA team. \cvskills{Python}
  \end{itemize}
  \item Staff augmentation, Health Care Services Provider -- Integration Team (\emph{US Client}),\\\cvdate{6}{2021}--\cvdate{10}{2021}
  \begin{itemize}
    \item Contributed to the development of software integration with external vendors. 
    \cvskills{Java, Spring Boot, JUnit5, Mockito, Kafka}
  \end{itemize}
\end{itemize}
\end{cvjob}

\begin{cvjob}
  \cvposition{Senior Software Developer Engineer}{Hipcam}
  \cvlocation{Montevideo, Uruguay}{\cvdate{11}{2018}}{\cvdate{10}{2020}}
  \begin{itemize}
    \item Joined the \emph{Cameras} group, contributing to the development and continuous improvement of Android firmware
    applications for Hipcam. \cvskills{Java, Kotlin, C/C++, Retrofit, OkHttp, Webhooks, Git}
    \item Led the re-implementation of the remote Android firmware applications update system, enhancing reliability and recovery options. 
    \cvskills{Java, Kotlin, C/C++, Retrofit, OkHttp, Webhooks, Git}
    \item Managed Jenkins Server for custom Android firmware applications builds, ensuring seamless collaboration across teams. 
    \cvskills{Jenkins, Docker}
  \end{itemize}
\end{cvjob}

\begin{cvjob}
  \cvposition{Software Developer Engineer}{Verifone}
  \cvlocation{Montevideo, Uruguay}{\cvdate{5}{2018}}{\cvdate{11}{2018}}
  \begin{itemize}
    \item Contributed to the \emph{Web} group, developing the management system for Verifone's internal customers. \cvskills{Java/JEE, PrimeFaces, Git}
    \item Developed automated tests for the management system and managed virtual machine images for testing. \cvskills{Java/JEE, Docker, Selenium}
  \end{itemize}
\end{cvjob}


\begin{cvjob}
  \cvposition{Java Software Developer}{Scanntech}
  \cvlocation{Montevideo, Uruguay}{\cvdate{8}{2014}}{\cvdate{4}{2018}}
  \begin{itemize}
    \item Contributed to the iPOS Android project, enhancing application logic, managing electronic payments, 
    and developing new device drivers. \cvskills{Java, SQLite, SVN, Git}
    \item Played a key role in the Scann+ project, designing a generic parser for fiscal printers used in Brazil. 
    Reduced development time by \emph{70\%}. \cvskills{Java, Git}
    \item Collaborated in developing microservices for monetary transactions with REST interfaces. 
    \cvskills{Python, Django, PostgreSQL, Git}
    \item Developed software for the \emph{MPOS PAX D200} pinpad. \cvskills{C/C++, CMake, libcurl, c-ares, Mbed TLS, Git}
    \item Integrated EMV transactions for the \emph{Pax S300} pinpad. \cvskills{C, Java, Git}
  \end{itemize}
\end{cvjob}

\begin{cvjob}
  \cvposition{Senior Support Technician for Servers and Networking}{Infoland}
  \cvlocation{Montevideo, Uruguay}{\cvdate{11}{2013}}{\cvdate{7}{2014}}
  
  \begin{itemize}
    \item Provided technical support to customers and internal team members. \cvskills{Windows Server, Linux}
    \item Contributed to the assembly, installation, and maintenance of networks, servers, and personal computers. \cvskills{Windows Server, Linux}
  \end{itemize}
\end{cvjob}

\newpage
\begin{cvjob}
  \cvposition{C++ Software Developer}{Segurmatica}  
  \cvlocation{Havana, Cuba}{\cvdate{3}{2011}}{\cvdate{6}{2013}}

  \begin{itemize}
    \item Key contributor to the Segurmatica Antivirus engine team, pioneering research and
    development of heuristic methods for malware detection. Successfully integrated these methods
    into Segurmatica Antivirus, achieving a consistent 5\% detection rate on malware samples. \cvskills{C++, Python, MSSQL, Git}
    
    \item Lead Author of \emph{"Addition of Heuristics Based on the Structure
    of the PE Files to Segurmatica Antivirus,"} presented at XV Convention and International Computer Fair
    2013. Highlighted the methodology and tools utilized to enhance Segurmatica Antivirus detection capabilities through heuristic methods.
    
    \item Contributed to the development of tools automating the processing of malware samples. \cvskills{C\#, Git}
  \end{itemize}
\end{cvjob}

\begin{cvjob}
  \cvposition{Software Developer and IT Specialist}{Tourism Real Estate Company}
  \cvlocation{Havana, Cuba}{\cvdate{10}{2008}}{\cvdate{2}{2011}}

  \begin{itemize}
    \item Developed centralized software for critical decision-making in real estate maintenance. \cvskills{Delphi, MSSQL, Mercurial}
    \item Contributed to Linux and Windows server administration, and MSSQL Server management. \cvskills{Ubuntu, Debian, Windows Server, MSSQL}
  \end{itemize}
\end{cvjob}

\begin{cvjob}
  \cvposition{Instructor}{Youth Clubs of Computing and Electronics}
  \cvlocation{Havana, Cuba}{\cvdate{10}{2006}}{\cvdate{9}{2008}}

  \begin{itemize}
    \item Instructed entry-level software development in \emph{Delphi} and \emph{Visual Basic}. \cvskills{Delphi, Visual Basic}
    \item Conducted user-level training in \emph{MS Windows}, \emph{MS Access}, and \emph{MS Excel}.
  \end{itemize}
\end{cvjob}

\begin{cvjob}
  \cvposition{Contract Developer}{Tanggo Software}
  \cvlocation{Remote}{\cvdate{6}{2006}}{\cvdate{9}{2006}}

  \begin{itemize}
    \item Designed and implemented \emph{Tanggo Gestione Gastronomica}, software for recipes management 
    and custom menu printing. \cvskills{Delphi, MS Access}
  \end{itemize}
\end{cvjob}

\begin{cvjob}
  \cvposition{Contract Developer}{Freelance}
  \cvlocation{Havana, Cuba}{\cvdate{5}{2005}}{\cvdate{8}{2005}}

  \begin{itemize}
    \item Developed \emph{Cafe Master}, software for stock management and sales recording for a small coffee shop. \cvskills{Delphi, MS Access}
  \end{itemize}
\end{cvjob}

\begin{cvjob}
  \cvposition{Scientist Intern}{Center of Radiation Protection and Hygiene}
  \cvlocation{Havana, Cuba}{\cvdate{9}{2004}}{\cvdate{9}{2006}}

  \begin{itemize}
    \item Completed thesis on software for dose estimation and potential effects on the embryo/fetus 
    due to maternal medical exposure. \cvskills{Delphi, MS Access}
    \item Joined the Research and Development Division post-graduation, contributing to various projects 
    in medical physics, evaluation, and internal contamination dose estimation. \cvskills{Delphi, MS Access}
    \item Taught radio diagnostic and internal contamination subjects to students of the 
    \emph{Higher Institute of Technologies and Applied Sciences}.
  \end{itemize}
\end{cvjob}

\end{cvexperience}

\begin{cvlang}
  \cvlangitem{Spanish}{Native}
  \cvlangitem{English}{Advanced, C1-C2}
\end{cvlang}

\end{document}
